First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei

### 2017-02-10 eg6-letters/coherent/dvcs_he4_prl.tex
start to implement Stepan's suggestions

%
\date{\today}
\begin{abstract}
We report the first fully exclusive measurement of deeply virtual Compton 
scattering (DVCS) off a nucleus for $A>1$. The experiment used the 6 GeV 
electron beam from Jefferson Lab projected onto a $^4$He target in the center 
of the CEBAF Large Acceptance Spectrometer (CLAS). An additional radial time 
projection chamber (RTPC) was used to detect the recoiling $^4$He nuclei and 
ensure the exclusivity of the process. We measured beam spin asymmetries 
significantly larger than that observed on proton targets and extracted,
in a completely model independent way, the chiral even generalized parton 
distribution (GPD) of the $^4$He nucleus. This pioneering measurement 
leads the way toward the 3D imaging of the partonic structure of nuclei.
\end{abstract}
\pacs{Valid PACS appear here}

>>>>

%
\date{\today}
\begin{abstract}
We report the first fully exclusive measurement of Deeply Virtual Compton 
Scattering (DVCS) off a nucleus for $A>1$. The experiment used the 6 GeV 
electron beam from CEBAF machine at Jefferson Lab projected onto a $^4$He gas 
target in the center of the CEBAF Large Acceptance Spectrometer (CLAS). A new 
radial time projection chamber (RTPC) was used to detect the recoiling $^4$He 
nuclei and ensure the exclusivity of the process. The measured Beam Spin 
Asymmetries (BSA) are significantly larger than that observed on the proton in 
the same kinematic domain. Since $^4$He is a spin zero target, we were able to 
extract, in a completely model independent way, chiral even Generalized Parton 
Distribution (GPD) H of $^4$He.

We measured beam spin asymmetries significantly larger than that observed on 
proton targets and extracted, in a completely model independent way, the chiral 
even generalized parton distribution (GPD) of the $^4$He nucleus. This 
pioneering measurement leads the way toward the 3D imaging of the partonic 
structure of nuclei.
\end{abstract}
\pacs{Valid PACS appear here}
